---
title: "team.Rmd"
names: "Ann Gould and Henry Underhill"
github: gould-ann, henryunderhill
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
choco <- read.csv("https://xdaiisu.github.io/ds202materials/hwlabs/choco.csv")
summary(choco)
```

# 1
```{r}
length(choco$Company)
```

# 2
```{r}
x <- table(choco$Review.Date)
barplot(x, main="# of Ratings vs Year", col=c("darkred", "darkblue", "green", "yellow", "purple"))
```

# 3
```{r}
#checking for 3 most frequent locations
location <- table(choco$Company.Location)
top3_countries <- sort(location, decreasing=TRUE)[1:3]
top3_countries

isTop3 <- choco$Company.Location == 'U.S.A.' | 
  choco$Company.Location == 'France' | choco$Company.Location == 'Canada'

table(isTop3)

countries <- choco[isTop3, ]
# head(countries)

plot(countries$Company.Location, countries$Rating)
```

# 4

Interesting question: What location has the best chocolate (based off of rating and company location)?

# 5
```{r}
library(dplyr)
                 
data <- choco %>%
  group_by(choco$Company.Location) %>%
  summarise(averageRating = mean(Rating))

# print(data)
print("best chocolate is in: ")
data[order("averageRating")][[1]][[1]]

```

# 6
Workflow: I'm unsure what Workflow means in this case. When it comes to writing code and the workflow associated with that, R Markdown is really easy to use to test increments of code instead of testing all code at once. A lot of this involved a lot of Google research and incrementally building out our solution from there. We were able to avoid merge conflicts by segmenting out the r chunks based on question (so creating an r chunk for each question and then dividing up questions) before both turning in our code.

Henry worked on questions 1 - 3, Ann worked on questions 4 - 6.
